Orientation Control System: Enhancing Aerial Maneuvers for Quadruped Robots

### 2023-01-04 mdpi2022roscia.tex
small modifications

\begin{table}[t!] 
	\caption{\MF{Physics related parameters used for simulate the robot dynamics in Gazebo}}
	\label{tab:pys_param}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CC}
		\toprule
		\textbf{Parameter} & \textbf{Value} \\
		\midrule
		Step size & $0.001 \ \mathrm{s}$\\
		Real time update rate & $250$ \\
		Physics engine & ODE \\
		Solver & Quick (Projected Gauss-Seidel method)\\
		Iterations & $50$\\
		Successive Over Relaxation parameter & $1.3$\\
		Rescaling Moment of Inertia  & no \\
		Friction model & Pyramid \\		
		\bottomrule	\end{tabularx}
\end{table}
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figures/drawing.png}
	\caption{\small First Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. A disturbance moment $\bm{\tau}_{dist}$ on the trunk can be compensated only if the \gls{ocs} is enabled. If it is disabled, the robot is unable to restore a safe configuration after the touch-down and eventually falls. The light blue area represents the interval of time in which the disturbance is applied.}
	\label{fig:fw_jump}
\end{figure}

\begin{figure}[t!]
	\centering
	\includegraphics[width=.7\linewidth]{figures/fall_plot.eps}
	\caption{\small Second Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. The \gls{ocs} drives the robot orientation during a fall to be horizontal. This allows to damp for damping the base oscillations after the touch-down (vertical dashed line), even without implementing a landing strategy}
	\label{fig:fall_plot}
\end{figure}
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{figures/backflip.png}
	\caption{\small \MF{Third Test: sequence of snapshots of Solo12 performing a back-flip in Gazebo environment. The \gls{ocs} alleviates the effort requested to the leg joints, that in this case can be used to accomplish only the vertical motion.}}
	\label{fig:backflip}
\end{figure}

>>>>

\begin{table}[t!] 
	\caption{\MF{Physics related parameters used for simulate the robot dynamics in Gazebo}}
	\label{tab:pys_param}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CC}
		\toprule
		\textbf{Parameter} & \textbf{Value} \\
		\midrule
		Step size & $0.001 \ \mathrm{s}$\\
		Real time update rate & $250$ \\
		Physics engine & Open Dynamics Engine (ODE) \\
		Solver & Quick (Projected Gauss-Seidel method)\\
		Iterations & $50$\\
		Successive Over Relaxation parameter & $1.3$\\
		Rescaling Moment of Inertia  & no \\
		Friction model & Pyramid \\		
		\bottomrule	\end{tabularx}
\end{table}
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figures/drawing.png}
	\caption{\small First Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. A disturbance moment $\bm{\tau}_{dist}$ on the trunk can be compensated only if the \gls{ocs} is enabled. If it is disabled, the robot is unable to restore a safe configuration after the touch-down and eventually falls. The light blue area represents the interval of time in which the disturbance is applied.}
	\label{fig:fw_jump}
\end{figure}

\begin{figure}[t!]
	\centering
	\includegraphics[width=.7\linewidth]{figures/fall_plot.eps}
	\caption{\small Second Test: simulation results showing the $\mathrm{CoM}_x$ and pitch trajectory vs. time plots. The \gls{ocs} drives the robot orientation during a fall to be horizontal. This allows to damp for damping the base oscillations after the touch-down (vertical dashed line), even without implementing a landing strategy}
	\label{fig:fall_plot}
\end{figure}
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{figures/backflip.png}
	\caption{\small \MF{Third Test: sequence of snapshots of Solo12 performing a back-flip in Gazebo environment. The \gls{ocs} alleviates the effort requested to the leg joints, that in this case can be used to accomplish only the vertical motion. The red, green and blue lines represent the axes of the inertial (world) reference frame.}}
	\label{fig:backflip}
\end{figure}
